### 2017-02-02 manuscript.rmd
moved simulations to man text, re knit from scratch

@@

			tree@data$Event = NA
			tree@data$Event[ tree@data$D == "N" ] = "Speciation"
			tree@data$Event[ tree@data$D == "Y" ] = "Duplication"

@@

@@

We examined the ensitivity of our results to the specification of calibration dates for the speciation nodes. In `r noised_replicate_n` reanalyses, we drew a new date for each calibration from a normal distribution with the mean of the original date and a standard deviation `r sd_fraction` times the original date. If any daugter nodes became older than their parent, we repeated the sampling until the dates were congruent with the topology. The minimum Wilcoxon p in these reanalyses was `r min( as.numeric( unlist( p_noised ) ) )`, *i.e.* none of them reject the null hypothesis that the rate of evolution of Tau is greater following duplication events than speciation events. This is consistent with the analysis that uses the calibration dates as specified, indicating that our results are robust to the selection of calibration times for speciation nodes.

#### Simulations

	sim_tau = function( nhx, dup_adjust=1 ) {

We first simulated a data set under the null model that tau evolves at the same rate following duplication and speciation events. Under the null model, pairwise analysis results (Figure XXSim a) are very similar as for the observed data, with higher rho for orthologs (`r ortholog_r_sim_null`) than paralogs (`r paralog_r_sim_null`). In the phylogenetic analysis of the null simulation, contrasts show similar divergence following speciation and duplication (Figure XXSim b) and does not reject the null hypothesis (Wilcoxon p=`r wilcox_oc( nodes_sim_null_contrasts )`).

>>>>

	#' Simulate Tau on a tree::treedata. Existing observed values are
	#' fit to a brownian model to estimate parameters. These parameters
	#' are then used to replace the original values with similated 
	#' values.
	#' 
	#' @param nhx A phylogenetic tree and associated Tau values 
	#' as a treeio::treedata object
	#' @param dup_adjust A multiplier for adjusting the branch lengths 
	#' following duplication to effectively change the rate following duplication
	#' @return A phylogenetic trees and simulated Tau values as a 
	#' treeio::treedata object
	#' @export
	sim_tau = function( nhx, dup_adjust=1 ) {

@@

			tree@data$Event = NA
			tree@data$Event[ tree@data$D == "N" ] = "Speciation"
			tree@data$Event[ tree@data$D == "Y" ] = "Duplication"
			tree@data$Event = factor( tree@data$Event, levels=c( "Speciation", "Duplication" ) )

@@

We simulated a data set under the null model that tau evolves at the same rate following duplication and speciation events. Under the null model, pairwise analysis results (Figure XXSim a) are very similar as for the observed data, with higher rho for orthologs (`r ortholog_r_sim_null`) than paralogs (`r paralog_r_sim_null`). In the phylogenetic analysis of the null simulation, contrasts show similar divergence following speciation and duplication (Figure XXSim b) and does not reject the null hypothesis (Wilcoxon p=`r wilcox_oc( nodes_sim_null_contrasts )`).

@@

We examined the sensitivity of our results to the specification of calibration dates for the speciation nodes. In `r noised_replicate_n` reanalyses, we drew a new date for each calibration from a normal distribution with the mean of the original date and a standard deviation `r sd_fraction` times the original date. If any daugter nodes became older than their parent, we repeated the sampling until the dates were congruent with the topology. The minimum Wilcoxon p in these reanalyses was `r min( as.numeric( unlist( p_noised ) ) )`, *i.e.* none of them reject the null hypothesis that the rate of evolution of Tau is greater following duplication events than speciation events. This is consistent with the analysis that uses the calibration dates as specified, indicating that our results are robust to the selection of calibration times for speciation nodes.
